\documentclass[10pt, letterpaper]{article}
\usepackage[
    ignoreheadfoot,
    top= 0.7cm,
    bottom=1cm,
    left=1cm,
    right=1cm,
    footskip=1.0 cm,
]{geometry}
\usepackage[explicit]{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\definecolor{primaryColor}{RGB}{0, 79, 144}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage[
    pdftitle={Muhammad HUZAIFA's CV},
    pdfauthor={Muhammad Huzaifa},
    pdfcreator={Huzaifa},
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref}
\usepackage[pscoord]{eso-pic}
\usepackage{calc}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{changepage}
\usepackage{paracol}
\usepackage{ifthen}
\usepackage{needspace}
\usepackage{iftex}

\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

\usepackage[default, type1]{sourcesanspro}
\AtBeginEnvironment{adjustwidth}{\partopsep0pt}
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\topskip}{0pt}
\setlength{\columnsep}{0.15cm}
\makeatletter
\titleformat{\section}{
    \needspace{4\baselineskip}
    \Large\color{primaryColor}
}{
}{
}{
    \textbf{#1}\hspace{0.15cm}\titlerule[0.8pt]\hspace{-0.1cm}
}[]

\titlespacing{\section}{
    -1pt
}{
    0.3 cm
}{
    0.2 cm
}

\newenvironment{highlights}{
    \begin{itemize}[
        topsep=0.10 cm,
        parsep=0.10 cm,
        partopsep=0pt,
        itemsep=0pt,
        leftmargin=0.4 cm + 10pt
    ]
}{
    \end{itemize}
}
\newenvironment{highlightsforbulletentries}{
    \begin{itemize}[
        topsep=0.10 cm,
        parsep=0.10 cm,
        partopsep=0pt,
        itemsep=0pt,
        leftmargin=10pt
    ]
}{
    \end{itemize}
}

\newenvironment{onecolentry}{
    \begin{adjustwidth}{
        0.2 cm + 0.00001 cm
    }{
        0.2 cm + 0.00001 cm
    }
}{
    \end{adjustwidth}
}
\newenvironment{twocolentry}[2][]{
    \onecolentry
    \def\secondColumn{#2}
    \setcolumnwidth{\fill, 4.5 cm}
    \begin{paracol}{2}
}{
    \switchcolumn \raggedleft \secondColumn
    \end{paracol}
    \endonecolentry
}

\newenvironment{threecolentry}[3][]{
    \onecolentry
    \def\thirdColumn{#3}
    \setcolumnwidth{1 cm, \fill, 4.5 cm}
    \begin{paracol}{3}
    {\raggedright #2} \switchcolumn
}{
    \switchcolumn \raggedleft \thirdColumn
    \end{paracol}
    \endonecolentry
}

\newenvironment{header}{
    \setlength{\topsep}{0pt}\par\kern\topsep\centering\color{primaryColor}\linespread{1.5}
}{
    \par\kern\topsep
}


\let\hrefWithoutArrow\href
\renewcommand{\href}[2]{\hrefWithoutArrow{#1}{\ifthenelse{\equal{#2}{}}{ }{#2 }\raisebox{.15ex}{\footnotesize \faExternalLink*}}}

\newcounter{projectcounter}
\newcommand{\projecttitle}[1]{\stepcounter{projectcounter}\Roman{projectcounter}. #1}
\begin{document}
\newcommand{\AND}{\unskip
	\cleaders\copy\ANDbox\hskip\wd\ANDbox
	\ignorespaces
}
\newsavebox\ANDbox
\sbox\ANDbox{}

\begin{header}
	\centering
	\fontsize{30pt}{30pt}\selectfont
	\textbf{Muhammad Huzaifa}

	\vspace{0.4cm}

	\normalsize
	\hrefWithoutArrow{mailto:theehuzaifa@gmail.com}{{\faEnvelope[regular]}\hspace{0.01cm} theehuzaifa@gmail.com} \quad
	{\faPhone*} \hspace{0.01cm} 0300-7005268 \quad
	\hrefWithoutArrow{https://muhammad-huzaifa-s-e.vercel.app}{{\faLink}\hspace{0.01cm} Portfolio} \quad
	\hrefWithoutArrow{https://www.linkedin.com/in/muhammad-huzaifa-ali-49aa94259/}{{\faLinkedinIn} \hspace{0.01cm}  Linkedin} \quad
	\hrefWithoutArrow{https://github.com/rogueinnovator}{{\faGithub}\hspace{0.01cm}  rogueinnovator} \quad
	{\faMapMarker*} Islamabad, Pakistan
\end{header}
\vspace{0.3 cm - 0.3 cm}
\section{Summary}
I am a Full-Stack Engineer with strong fundamentals in JavaScript and TypeScript, focusing on the MERN stack and Next.js. I specialize in building robust REST APIs, scalable backend logic with Node.js/Express.js, and dynamic frontends using React functional components, hooks, and state management.\\[4pt]
Lately, I've also focused on practical AI integrations, building custom RAG pipelines, vector databases, and reliable backend architectures that solve real business problems. I am highly comfortable working in Agile/Scrum environments with active participation in sprint planning and daily standups.\\[4pt]
Beyond just writing code, I consider myself a product builder. I love taking ownership of the entire development cycle, from database schema design and indexing to containerizing apps with Docker and ensuring high code quality through rigorous Git workflows, PRs, and code reviews.

\section{Skills}
\begin{highlights}
	\item \textbf{Programming Languages:} JavaScript (ES6+), TypeScript, PHP, C++, Solidity
	\item \textbf{Frontend Development:} React.js, Next.js, Redux, Svelte, Tailwind CSS, Blade
	\item \textbf{Backend Development:} Node.js (Express.js), Laravel, REST APIs, WebSockets, Microservices, SSE
	\item \textbf{Databases \& Caching:} MySQL, PostgreSQL, MongoDB (NoSQL), Redis, Supabase
	\item \textbf{Testing \& CI/CD:} GitHub for PRs, version control, CI/CD practices
	\item \textbf{Tools \& Practices:} DevOps, Docker, Agile/Scrum, Postman
	\item \textbf{Cloud \& Deployment:} AWS (S3, SQS, Lambda, EC2), AWS Lightsail, Vercel, Render
	\item \textbf{Mobile :} React Native, Expo,
	\item \textbf{AI \& GenAI:} OpenAI API, RAG Pipelines, Vector Embeddings
	\item \textbf{Blockchain/Web3:} Ethereum, Web3.js, Ethers.js, Hardhat, Truffle, Ganache, Smart Contracts
	\item \textbf{Development Tools:} Git, GitHub, Docker, LaTeX, Postman
	\item \textbf{Deployment:} AWS EC2, AWS Lightsail, Vercel, Render, Linode
	\item \textbf{Operating Systems:} Linux
\end{highlights}
% Experience
\section{Experience}
\begin{twocolentry}{
    G13/4, Islamabad\\
    \textit{ May 2025 - Present}
}
\textbf{Red Star Technologies — MERN Stack Developer}
\begin{highlights}
    \item Delivered high-quality, client-focused solutions across multiple projects as a MERN and Next.js developer.
    \item Successfully closed and retained multiple clients through consistent delivery of robust and scalable applications.
    \item Integrated AI-driven features into various client projects, enhancing functionality and user experience.
    \item Maintained a strong professional reputation through reliability, technical expertise, and commitment to excellence.
\end{highlights}
\end{twocolentry}

\begin{twocolentry}{
		Satellite Town, Rawalpindi\\
		\textit{Nov 2024 - May 2025}
	}
	\textbf{Code Crush — MERN Stack Developer}
	\begin{highlights}
		\item Engineered 4 full-stack web applications utilizing the MERN stack to deliver robust user experiences.
		\item Constructed RESTful APIs using Express.js, ensuring efficient data exchange with React frontends.
		\item Architected scalable backend logic incorporating MVC methodologies, TypeScript, and ES modules.
	\end{highlights}
\end{twocolentry}


\begin{twocolentry}{
		JB Tower, Peshawar \\
		\textit{June 2024 - Nov 2024}
	}
	\textbf{OIRRC — Junior web Developer}
	\begin{highlights}
		\item Authored scalable full-stack applications using \textbf{Next.js}, seamlessly managing client-side and server-side business logic.
		\item Administered relational databases using \textbf{PostgreSQL} to guarantee optimized data storage and rapid retrieval.
		\item Configured \textbf{Prisma ORM} for streamlined schema modeling, reliable migrations, and performant backend queries.
	\end{highlights}
\end{twocolentry}


\section{Projects}
\vspace{1em}

\begin{twocolentry}{
		\href{http://osglobal.ownersjungle.com/}{Live(staging)}
	}{
		\textbf{\projecttitle{Owners Global \& Owners Inventory}}
	}
\begin{highlights}
    \item Architected a multi-app ecosystem where \textbf{Owners Global} securely provisions and shares organizational data with the \textbf{Owners Inventory} client.
    \item Constructed the \textbf{Owners Inventory} interface leveraging \textbf{Laravel} and \textbf{Blade} templates for dynamic server-rendered views.
    \item Integrated Server-Sent Events (SSE) to broadcast real-time progress indicators for extended asynchronous server operations.
    \item Engineered a custom SSO solution for frictionless authentication, centralizing the core authorization logic in \textbf{Node.js} while routing redirection paths via \textbf{PHP}.
	\item Orchestrated secure multi-platform invite workflows and seamlessly hooked into the Stripe payment gateway processing.
    \item Configured and executed CI/CD deployment pipelines targeting a high-availability production environment on \textbf{AWS Lightsail}.
    \item \textbf{Technologies:} PHP, Laravel, Blade, MySQL, Node.js, TypeScript, AWS (Lightsail, S3, SQS).
\end{highlights}
\end{twocolentry}
\vspace{1em}

% Klic
\begin{twocolentry}{
		\href{https://dev.klic.gg}{Live}
	}{
		\textbf{\projecttitle{Klic (Streaming Web App)}}
	}
	\begin{highlights}
    \item Restructured both backend and frontend architectures, significantly boosting query performance, overall scalability, and long-term maintainability.
    \item Diagnosed and eradicated critical production bugs, elevating application stability and maintaining high client retention.
    \item Established stringent protocols for code quality assurance, strict version control, and automated continuous delivery.
    \item \textbf{Technologies:} Next.js, GraphQL, SCSS, Node.js, TypeScript, Redux, AWS services.
\end{highlights}
\end{twocolentry}
\vspace{1em}
% Owner super admin
\begin{twocolentry}{
		\href{https://osfrontend.ownersjungle.com/owner-inventory/dashboard}{Live}
	}{
		\textbf{\projecttitle{Owner Super Admin}}
	}
\begin{highlights}
    \item Streamlined backend modules for seamless connectivity with remote instances and \textbf{AWS RDS} operations leveraging an OOP-based pattern.
    \item Formulated user impersonation functionalities, greatly expanding administrative oversight and troubleshooting capabilities.
    \item Enforced industry standards for software quality, repository management, and zero-downtime deployment workflows.
    \item Troubleshot pervasive UI components and backend defects, solidifying system reliability for end-users.
    \item \textbf{Technologies:} Next.js, Tailwind CSS, Node.js, TypeScript, Redux, AWS Services.
\end{highlights}
\end{twocolentry}
\vspace{1em}

% Kolabme
\begin{twocolentry}{
		\href{https:app.kolabme.com}{Live}
	}{
		\textbf{\projecttitle{KolabMe (A health care platform)}}
	}
	\begin{highlights}
    \item Spearheaded a comprehensive telemedicine platform empowering users to schedule physician appointments, update health records, and conduct virtual consultations.
    \item Incorporated real-time WebSocket messaging to facilitate instant, secure chat interactions between medical professionals and patients.
    \item Designed an extensive administrative dashboard for centralizing the management of personnel, patient scheduling, and communications.
    \item \textbf{Technologies:} React.js, Node.js, Express.js, Websockets, AWS, Redux.
\end{highlights}
\end{twocolentry}
\vspace{1em}
\begin{twocolentry}{
		\href{https://leyloon.com/}{Live}
	}{
		\textbf{\projecttitle{Leyloon}}
	}
\begin{highlights}
    \item Launched a premium e-commerce platform allowing users to seamlessly browse and customize bespoke moissanite and lab-grown diamond jewelry.
    \item Programmed a sophisticated visual design engine enabling granular customer selection of stone types, gem shapes, carat sizes, and metals.
    \item Embedded an \textbf{AI jeweler} assistant to interactively guide customers through the personalized rendering and design life cycle.
    \item \textbf{Technologies:} Next.js, Next.js API Routes, TanStack Query, Radix UI, NodeMailer, Anime.js, Context API, VDB API.
\end{highlights}
\end{twocolentry}
\vspace{1em}
% On point
\begin{twocolentry}{
		\href{onpointwebapp.vercel.app/}{Live}
	}{
		\textbf{\projecttitle{On Point}}
	}
	\begin{highlights}
		\item Crafted a full-stack web wrapper for IRISCRM, independently orchestrating complex business rules and real-time CRM data integration.
		\item Scheduled automated background cron jobs via \textbf{Inngest} for monthly deal imports and dynamic calculations of sales representative targets.
        \item Deployed a companion mobile application utilizing \textbf{React Native} and \textbf{Nativewind}, consuming backend APIs for a seamless cross-device CRM workflow.
		\item \textbf{Technologies:} Next.js, React Native, Nativewind, Inngest, Tailwind CSS, IRIS APIs.
	\end{highlights}
\end{twocolentry}
\vspace{1em}
% Blockchain-Based Criminal Information Management System

% Decentralized Chatting App
% \begin{twocolentry}{
% 		\href{https://github.com/rogueinnovator/d-chat-app}{GitHub}
% 	}{
% 		\textbf{\projecttitle{Decentralized Chatting App}}
% 	}
% 	\begin{highlights}
% 		\item Built a secure, blockchain-based messaging platform ensuring decentralized communication.
% 		\item Implemented smart contract logic for real-time message validation and storage.
% 		\item \textbf{Technologies:} Next.js, Hardhat, CSS.
% 	\end{highlights}
% \end{twocolentry}
% \vspace{1em}
\begin{twocolentry}{
		\href{https://rogue-innovator.vercel.app/}{Live}
	}{
		\textbf{\projecttitle{Web base Linux inspired OS}}
	}
	\begin{highlights}
		\item \textbf{Advanced Window Management:} Scripted custom logic to facilitate fluid drag-and-drop mechanics and precise 8-direction window resizing.
		\item \textbf{Terminal Integration:} Embedded Xterm.js to simulate a robust terminal environment supporting standard shell execution and file navigation.
		\item \textbf{AI Assistant:} Integrated a Gemini-powered conversational chatbot to autonomously answer queries regarding my technical expertise.
		\item \textbf{Simulated OS Showcase:} Pioneered a unique, interactive operating system simulation to gamify and exhibit my professional portfolio.
		\item \textbf{Technologies:} Xterm, Svelte, Scss, Gemini API.
	\end{highlights}
\end{twocolentry}
\vspace{1em}


% AI-Powered Proposal Generator
\begin{twocolentry}{
	}{
		\textbf{\projecttitle{AI-Powered Proposal Generator \& Portfolio Assistant}}
	}
\begin{highlights}
    \item Architected a RAG-enhanced reasoning system featuring multiple pipelines to autonomously formulate personalized, high-converting client proposals.
    \item Formulated an asynchronous background ingestion queue using Inngest and OpenAI to distill and vectorize project datasets directly into a Supabase pgvector instance.
    \item Devised an autonomous Q\&A chat interface for semantic portfolio queries, fortified with strict anti-hallucination guardrails and zero-jargon algorithms.
    \item \textbf{Technologies:} Next.js, React 19, Supabase, PostgreSQL, pgvector, OpenAI API, Inngest, Tailwind CSS, shadcn/ui.
\end{highlights}
\end{twocolentry}
\vspace{1em}

% Other Notable Projects
\begin{twocolentry}{
	}{
		\textbf{\projecttitle{Other Notable Projects}}
	}
	\begin{highlights}
		\item \href{https://nomacal.com}{Nomacal} $\vert$ \href{https://creme-xchange.vercel.app/signin}{CremeXchange} $\vert$ \href{https://govio.ai/}{Govio} $\vert$ \href{https://www.aramtours.de/}{Aram Tours} $\vert$ \href{https://e-help-ochre.vercel.app/}{E-Help}
	\end{highlights}
\end{twocolentry}

\section{Education}

\begin{threecolentry}{}{
		2020 – 2024
	}
	\textbf{Bachelor of Computer Science} \\
	\textbf{University of Peshawar }\\
	Relevant Coursework: Data Structures, Algorithms, Database Systems, Web Development, Blockchain Fundamentals
\end{threecolentry}

% \section{Certifications}
% \begin{highlights}
% 	\item \textbf{Blockchain Developer Nanodegree} - Udacity (2023)
% 	\item \textbf{AWS Certified Cloud Practitioner} - Amazon Web Services (2023)
% 	\item \textbf{Full Stack Web Development} - Code Crush (2022)
% \end{highlights}


\end{document}